Continuous developmental changes in word recognition across early childhood support early language learning

### 2025-02-05 paper/paper.Rmd
sem aesthetic tweaks

node_text <- tribble(~name, ~ pretty, ~fill, 
                     "acc_t0", "t0 Accuracy", "lightblue",
                     "acc_t1", "t1 Accuracy", "lightblue",
                     "acc_t2", "t2 Accuracy","lightblue",
                     "acc_t3", "t3 Accuracy","lightblue",
                     "acc_t4", "t4 Accuracy","lightblue",
                     "accuracy_intercept", "Accuracy intercept","lightblue",
                     "accuracy_slope", "Accuracy slope","lightblue",
                     "log_rt_t0", "t0 log RT","pink",
                     "log_rt_t1", "t1 log RT","pink",
                     "log_rt_t2", "t2 log RT","pink",
                     "log_rt_t3", "t3 log RT","pink",
                     "log_rt_t4", "t4 log RT","pink",
                     "prod_t0" , "t0 Production", "lightgreen",
                     "prod_t1" , "t1 Production",  "lightgreen",
                     "prod_t2" , "t2 Production" ,  "lightgreen",
                     "prod_t3", "t3 Production",          "lightgreen",
                     "prod_t4", "t4 Production" , "lightgreen",
                     "speed_intercept" , "Speed intercept" ,  "pink",
                     "speed_slope" , "Speed slope","pink",
                     "vocab_intercept", "Vocabulary intercept", "lightgreen",
                     "vocab_slope", "Vocabulary slope",  "lightgreen" ) |> 
  mutate(alpha=.5)

@@

edges <- get_edges(slopes_long) |> mutate(label_location=.5) |> mutate(label=ifelse(arrow=="last", NA, label)) |>  mutate(connect_from=ifelse(to==from, "right",NA),
                    connect_to=connect_from) |> 
  mutate(color="black", label_hjust=.5, label_location=.5)

edges[52,"curvature"]=85
edges[52,"color"]="blue"
edges[61,"curvature"]=85
edges[61,"color"]="blue"
edges[66,"curvature"]=85
edges[66,"color"]="blue"
edges[52, "label_hjust"]=0
edges[61, "label_hjust"]=0
edges[66, "label_hjust"]=0

@@

edges[53,"curvature"]=80
edges[53,"color"]="red"
edges[55,"curvature"]=82
edges[55,"label_location"]=.55

edges[55,"color"]="red"
edges[62,"curvature"]=80
edges[62,"color"]="red"
edges[53, "label_location"]=.6
edges[53, "label_hjust"]=0.4

edges[58,"curvature"]=80
edges[58,"color"]="darkgreen"
edges[60,"curvature"]=82
edges[60,"color"]="darkgreen"
edges[60,"label_location"]=.45
edges[65,"curvature"]=80
edges[65,"color"]="darkgreen"
edges[65, "label_location"]=.4
edges[53, "label_hjust"]=0.4

>>>>

acc_color <- "#B2DF8A"
rt_color <- "#FB9A99"
prod_color <- "#FFFF99"

intercept_color <- "#1F78B4"
intercept_background <- "#A6CEE3"
slope_color <- "#FF7F00"
slope_background <- "#FDBF6F"

#"#A6CEE3" "#1F78B4" "#B2DF8A" "#33A02C"
# [5] "#FB9A99" "#E31A1C" "#FDBF6F" "#FF7F00"
# [9] "#CAB2D6" "#6A3D9A" "#FFFF99" "#B15928"
node_text <- tribble(~name, ~ pretty, ~fill, 
                     "acc_t0", "t0 Accuracy", acc_color,
                     "acc_t1", "t1 Accuracy", acc_color,
                     "acc_t2", "t2 Accuracy",acc_color,
                     "acc_t3", "t3 Accuracy",acc_color,
                     "acc_t4", "t4 Accuracy",acc_color,
                     "accuracy_intercept", "Accuracy intercept",acc_color,
                     "accuracy_slope", "Accuracy slope",acc_color,
                     "log_rt_t0", "t0 log RT",rt_color,
                     "log_rt_t1", "t1 log RT",rt_color,
                     "log_rt_t2", "t2 log RT",rt_color,
                     "log_rt_t3", "t3 log RT",rt_color,
                     "log_rt_t4", "t4 log RT",rt_color,
                     "prod_t0" , "t0 Production", prod_color,
                     "prod_t1" , "t1 Production",  prod_color,
                     "prod_t2" , "t2 Production" ,  prod_color,
                     "prod_t3", "t3 Production",         prod_color,
                     "prod_t4", "t4 Production" , prod_color,
                     "speed_intercept" , "Speed intercept" , rt_color,
                     "speed_slope" , "Speed slope",rt_color,
                     "vocab_intercept", "Vocabulary intercept", prod_color,
                     "vocab_slope", "Vocabulary slope",  prod_color ) |> 
  mutate(alpha=.1)

@@

edges <- get_edges(slopes_long) |> mutate(label_location=.5) |> mutate(label=ifelse(arrow=="last", NA, label)) |>  mutate(connect_from=ifelse(to==from, "right",NA),
                    connect_to=connect_from) |> 
  mutate(color="black", label_hjust=.5, label_location=.5, label_fill="white")

edges[52,"curvature"]=85
#edges[52,"color"]="blue"
edges[61,"curvature"]=85
#edges[61,"color"]="blue"
edges[66,"curvature"]=85
#edges[66,"color"]="blue"
edges[52, "label_hjust"]=0
edges[61, "label_hjust"]=0
edges[66, "label_hjust"]=0

@@

edges[53,"curvature"]=80
edges[53,"color"]=intercept_color
edges[53, "label_fill"]=intercept_background
edges[55,"curvature"]=82
edges[55,"label_location"]=.55

edges[55,"color"]=intercept_color
edges[55, "label_fill"]=intercept_background

edges[62,"curvature"]=80
edges[62,"color"]=intercept_color
edges[62, "label_fill"]=intercept_background

edges[53, "label_location"]=.6
edges[53, "label_hjust"]=0.4

edges[58,"curvature"]=80
edges[58,"color"]=slope_color
edges[58, "label_fill"]=slope_background

edges[60,"curvature"]=82
edges[60,"color"]=slope_color
edges[60, "label_fill"]=slope_background
edges[60,"label_location"]=.45
edges[65,"curvature"]=80
edges[65,"color"]=slope_color
edges[65, "label_fill"]=slope_background
edges[65, "label_location"]=.4
edges[53, "label_hjust"]=0.4
